Q1: Are lake and terrestrial primary productivity coherent?

### 2019-12-10 AnalysisCode/Q1_coherenceSpatialVariation/ms1_prep.Rmd

accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
maxndvi<-mask(maxndvi,watermask,maskvalue=0)

analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")

>>>>

accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
#maxndvi<-mask(maxndvi,watermask,maskvalue=0)

analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
#analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_2.RData")
